Low load operating protocol investigation of a 620MWe power boiler using a fast Eulerian-Eulerian CFD model

### 2021-09-06 PAPER_2/PAPER_2_REV1.tex
Update - 06/09/2021

\section{Introduction}

@@

\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\label{fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\linewidth}{p{0.35\linewidth} XXXXXX}
\hline
&\multicolumn{6}{c}{Cases}\\
 & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
\hline
\textbf{Main steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
\textbf{Main steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
\textbf{RH steam flow rate} [$kg/s$]&162&172&182&164&174&184\\
\textbf{RH steam exit temp} [$^{\circ}C$]&162&172&182&164&174&184\\
\textbf{Boiler efficiency} [$\%$]&162&172&182&164&174&184\\
\textbf{Attemperator 1} [$kg/s$]&162&172&182&164&174&184\\
\textbf{Attemperator 2} [$kg/s$]&162&172&182&164&174&184\\
\textbf{Attemperator RH} [$kg/s$]&162&172&182&164&174&184\\
\textbf{Platen wall temp (mean,min,max)} [$^{\circ}C$] &162&172&182&164&174&184 \\
\textbf{Pendant wall temp (mean,min,max)} [$^{\circ}C$]&162&172&182&164&174&184  \\
\hline
\end{tabularx}}
\end{table}

>>>>

\section{Introduction}
In the beginning the giant penguins of south east asia used to hunt the great walri of svenborg.

@@

\begin{figure}[h!]
\centering
\subfigure[]{\includegraphics[scale = 0.36]{SYMMETRY_PROBE_COPPM}}
\hspace{5mm}
\subfigure[]{\includegraphics[scale = 0.36]{OFFSET_PROBE_COPPM}}\\
\subfigure[]{\includegraphics[scale = 0.35]{SYMMETRY_PROBE_XO2}}
\hspace{5mm}
\subfigure[]{\includegraphics[scale = 0.35]{OFFSET_PROBE_XO2}}

\caption{bye}
\end{figure}

\begin{table}[h!]
\centering
\caption{Process model control parameters}
\label{fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
\hline
&\multicolumn{6}{c}{Cases}\\
 & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
\hline
\textbf{Main steam flow rate} 	[$kg/s$]		&166&163&170	&171&169&163\\
\textbf{Main steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&535&535\\
\textbf{RH steam flow rate} 	[$kg/s$]		&150&148&154	&154&153&147\\
\textbf{RH steam exit temp} 	[$^{\circ}C$]	&535&535&535	&535&520&490\\
\textbf{Boiler efficiency} 		[$\%$]			&86.2&84.9&88.8	&88.2&86.6&82.2\\
\textbf{Attemperator 1} 		[$kg/s$]			&10.5&15&16		&11.5&9.5&12\\
\textbf{Attemperator 2} 		[$kg/s$]			&5&8&5			&4&5&5.5\\
\textbf{Attemperator RH} 		[$kg/s$]			&0.5&1&1		&0&0&0\\
\hline
\end{tabularx}}
\end{table}

\begin{table}[h!]
\centering
\caption{Platen and pendant wall temperatures}
\label{fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\linewidth}{p{0.45\linewidth} XXXXXX}
\hline
&\multicolumn{6}{c}{Cases}\\
 & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
\hline
\multicolumn{7}{l}{\textit{Platen SH}}\\
\textbf{Max wall temperature} [$K$]  &754 & 750 & 765 & 766 & 753 & 763\\
\textbf{Mean wall temperature} [$K$] &726 & 712 & 719 & 727 & 715 & 724\\
\multicolumn{7}{l}{\textit{Pendant SH}}\\
\textbf{Max wall temperature} [$K$]  & 805 & 807 & 811 & 808 & 800 & 802\\
\textbf{Mean wall temperature} [$K$] & 793 & 786 & 792 & 795 & 788 & 784\\
\hline
\end{tabularx}}
\end{table}

\begin{equation}
T_{metal} = T_{wall} - \left(\frac{\dot{q}_{SH}t_{ASH}}{\lambda_{ASH}}\right)
\end{equation}

\begin{table}[h!]
\centering
\caption{Radiative heat transfer percentage for the platen and pendant SH}
\label{fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\linewidth}{p{0.25\linewidth} XXXXXX}
\hline
&\multicolumn{6}{c}{Cases}\\
 & \textbf{1} & \textbf{2} & \textbf{3}& \textbf{4}&\textbf{5}&\textbf{6}\\
\hline
Platen SH [\%] & 91.6 & 94.1 & 92.5 & 92.6 & 93.9 & 93.4\\
Pendant SH [\%] & 92.8 & 92.7 & 93.5 & 93.4 & 92.7 & 94.1\\
\hline
\end{tabularx}}
\end{table}
